What makes musicians infer teaching intentions?

### 2023-01-06 paper/manuscript.Rmd
update docx file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
# packages
if (!require("papaja")) {install.packages("papaja"); require("papaja")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("magick")) {install.packages("magick"); require("magick")}

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r set-up, include = FALSE}
# packages
if (!require("papaja")) {install.packages("papaja"); require("papaja")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("magick")) {install.packages("magick"); require("magick")}
